Exoplanet population inferences from a hierarchical model of the \kepler\ ``Object of Interest'' Catalog

### 2013-11-21 document/ms.tex
typo

\title{%
    Exoplanet population inferences
    from a hierarchical model
    of the \Kepler\ ``Object of Interest'' Catalog
}

@@

\begin{abstract}
The catalog of \Kepler\ Objects of Interest (KOI) is a list of putative periodic exoplanet transit signals
  discovered in the photometric data from the \Kepler Satellite.
In principle this catalog contains a wealth of statistical information about the full population of exoplanets.
Here we construct a model of the population that explains the content of the catalog.
Our approach is novel in that
  it takes the form of a rigorous (if approximate) hierarchical Bayesian inference,
  it includes a parameterization of a non-trivial selection function (incompleteness),
  and we fully marginalize out all latent and nuisance parameters using sampling.
Because the model is properly hierarchical,
  it can be constrained by multiple data sources;
  we demonstrate this by adding the Solar System as a constraint,
  but extensions to radial velocity, direct detection, and astrometric surveys would also be straightforward.
Approximations abound:
  Simple parameterized forms are assumed for the multivariate distribution of exoplanet parameters,
  incompleteness is assumed to depend only on a scalar related to signal-to-noise,
  and the KOI catalog is assumed to be dominated by real (not false-positive) exoplanet signals.
We find XXX and YYY.
\end{abstract}

>>>>

\title{%
    Exoplanet population inferences
    from a hierarchical model
    of the \kepler\ ``Object of Interest'' Catalog
}

@@

\begin{abstract}
The catalog of \kepler\ Objects of Interest (KOI) is a list of putative periodic exoplanet transit signals
  discovered in the photometric data from the \kepler Satellite.
In principle this catalog contains a wealth of statistical information about the full population of exoplanets.
Here we construct a model of the population that explains the content of the catalog.
Our approach is novel in that
  it takes the form of a rigorous (if approximate) hierarchical Bayesian inference,
  it includes a parameterization of a non-trivial selection function (incompleteness),
  and we fully marginalize out all latent and nuisance parameters using sampling.
Because the model is properly hierarchical,
  it can be constrained by multiple data sources;
  we demonstrate this by adding the Solar System as a constraint,
  but extensions to radial velocity, direct detection, and astrometric surveys would also be straightforward.
Approximations abound:
  Simple parameterized forms are assumed for the multivariate distribution of exoplanet parameters,
  incompleteness is assumed to depend only on a scalar related to signal-to-noise,
  and the KOI catalog is assumed to be dominated by real (not false-positive) exoplanet signals.
We find XXX and YYY.
\end{abstract}
